---
title: "Presentation practice (week 3 assignment)"
author: "MM Chien"
date: "December 22, 2017"
output: ioslides_presentation
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(plotly)
library(tidyr)
library(lubridate)
```

## Introduction

This is the data of virus isolation from patients with upper respiratory tract infection in Taiwan. Data was provided on Taiwan CDC website

```{r, echo=FALSE}
dat <- read.csv("virus.csv")
colnames(dat)[1] <- "Yearweek"
dat<- dat[,1:7]  ##remove the last variable, which is the positive yield rate
dat.long <- gather(dat, virus, yieldno, -Yearweek)
dat.long2 <- separate(dat.long, Yearweek, into=c("Year","Week"), sep=4)
```

## Virus type
- Most common upper respiratory tract infection virus type are as below:

    + RSV
    + Parainfluenza
    + CMV
    + Adenovirus
    + Influenza

## Yield with virus

We can see that the most common respiratory tract virus yielded is still influenza, follow by parainfluenza.
```{r, echo=FALSE, warning=FALSE}
plot_ly(dat.long2, x=~Week, y=~yieldno, type="bar", color=~virus)
```

## Influenza in 2016 and 2017
Comparing 2016 with 2017

```{r, echo=FALSE, warning=FALSE}
dat.influenza <- subset(dat.long2, virus=="Influenza")
plot_ly(dat.influenza, x=~Week, y=~yieldno, type="bar", color=~Year)
```
